\section{Hardware}

The ASV's frame is built from two 4" PVC pipes, each 30" long, mounted in parallel to provide flotation and structural support. A block of closed-cell EPS foam is secured beneath the pipes to improve buoyancy and overall water stability, as well as introducing some rigidity to the system. A closed cell foam was required for underwater use, as open cell foam would absorb water and lose its buoyancy. The foam was cut to fit the frame and held in place with 8 (1/4") bolts and nuts. A 24" wide platform is built on top of the PVC pipes, consisting of two (1/8") MDF wooden sheets for rigidity and a polycarbonate sheet for mounting structural components. Polycarbonate was chosen for its strength and durability, but it is very flexibe. The purpose of the MDF and EPS foam was to provide more of a rigid base, while the polycarbone sheet is used as a very strong mounting surface. 

The bouyancy in kilograms is calculated using the following equation:
\begin{equation}
    \text{Buoyancy} = \text{Weight of water displaced} = \text{Volume of submerged object} \times \text{Density of water}
\end{equation}

A waterproof enclosure is mounted at the center of the platform to protect onboard systems. Above it, a 100W solar panel is held in place by four pairs of custom 3D-printed brackets. The brackets attach to the four corners of the solar panel, and then are attached to the base of the boat via a 10" long (1/4") fiberglass composite rod, which is seated inside of the other piece of the bracket. These brackets were strong enough to hold the solar panel in place, but further iterations could add a set screw into each mount to ensure that the rods do not slip out of the brackets, as it is currently held in place by friction and the weight of the solar panel. These brackets allow for easy removal of the solar panel for ease of transportation. An assembly view of the solar panel mount can be seen below in Figure (INSERT FIG HERE, NOT DOING IT NOW AS TO NOT BREAK LATEX).

The motor is mounted at the stern using a custom 3D-printed flange. The flange is designed to fit a 1" PVC pipe which connects the motor to the frame, and keeps the PVC shaft vertical during operation. There are custom 3D printed brackets on either side of the PVC pipe to attach the motor to the PVC pipe on the bottom, and to attach the servo to the PVC pipe on the top. To keep the motor in place, two 3D printed bushing were designed to fit the PVC shaft, which keep the motor at a constant depth. The bushing rotate above the flange, but the coefficient of friction between the two is low enough to allow the motor to rotate freely. This design choice ensures that the motor remains securely in place during operation, even in rough water conditions. The choice of a friction based bushing and flange system was chosen over a bearing system to reduce cost and complexity, as well as to allow for easy replacement of parts if needed. The bushing is designed to be easily replaceable, allowing for quick maintenance and repairs.

Material choice for 3D printed parts was given careful consideration to ensure the ASV is lightweight, low cost, but also resistant to wear. The 3D printed Flange is made from ASA, a material known for its excellent UV resistance and mechanical properties. All other parts were made from PETG, which is a strong and durable material that maintains its structure underwater, making it suitable for the ASV's environment. The use of these materials ensures that the ASV can withstand the rigors of outdoor use while remaining lightweight and cost-effective. Structural parts were printed using 5 perimters and 25\% gyroid infill, which provided a good balance of strength and weight, while also keeping costs relatively low. The entire project used under 750g of PETG, and around 250g of ASA, which can be purchased for around \$15. Further iterations could likely halve this number.